Constraining the Distances and Physical Properties of Semiresolved Galaxies with Simulation Based Inference

### 2023-12-12 src/tex/ms.tex
[showyourwork] overleaf sync

In order to produce mock images with realistic noise profiles we inject them into real data. Using \artpop{} we first render pristine, i.e. noise free, images that have been convolved to the PSF and pixel scale of the specified survey. Then we add Poisson noise before injecting these images into patches of real data. We do not pre-select "empty" regions as we want to pass the full distribution of data quality to the network such that it can produce realistic uncertainties.
\begin{figure}
    \centering
    \includegraphics{figures/Pal4_post_corner.pdf}
    \caption{Caption}
    \label{fig:test}
\end{figure}

@@

\begin{table*}
    \centering
    \caption{The parameters are priors for our SSP model parameterized used to model globular clusters}
    \small
    \begin{tabular}{c c c} 
        Parameter & Description & Prior \\  \hline \hline
         D & Distance to galaxy (kpc) & Uniform: $D_{\rm min}$ -  $D_{\rm max}$ (User Specified) \\
         $\log (M_*/M_\odot)$ & Total Stellar Mass & Log-uniform: $M_{\rm*, min}$ -  $M_{\rm* , max}$ (User Specified) \\
         $Z$ & Metallicity parameterized as [Fe/H] & Uniform: $-2.25-0.25$ \\
         $Age$& Age of the the SSP (Gyr) & Uniform: $5-12$\\ \hline
    \end{tabular}
    \label{tab:ssp_model}
\end{table*}
\subsection{Dwarfs in the Sculptor Group}
\label{sec:scul}
\subsection{Galaxies in HSC}
\label{sec:hsc}

>>>>

In order to produce mock images with realistic noise profiles we inject them into real data. Using \artpop{} we first render pristine, i.e. noise free, images that have been convolved to the PSF and pixel scale of the specified survey. Then we add Poisson noise before injecting these images into patches of real data. We do not pre-select "empty" regions as we want to pass the full distribution of data quality to the network such that it can produce realistic uncertainties.

@@

\begin{table*}
    \centering
    \caption{The parameters are priors for our SSP model parameterized used to model globular clusters}
    \small
    \begin{tabular}{c c c} 
        Parameter & Description & Prior \\  \hline \hline
         D & Distance (kpc) & Uniform: $D_{\rm min}$ -  $D_{\rm max}$ (User Specified) \\
         $\log (M_*/M_\odot)$ & Total Stellar Mass & Log-uniform: $M_{\rm*, min}$ -  $M_{\rm* , max}$ (User Specified) \\
         $Z$ & Metallicity parameterized as [Fe/H] & Uniform: $-2.25-0.25$ \\
         $Age$& Age of the the SSP (Gyr) & Uniform: $5-12$\\ \hline
    \end{tabular}
    \label{tab:ssp_model}
\end{table*}

\begin{figure*}
    \centering
    \includegraphics[width=0.45\textwidth]{figures/Pal4_post_corner.pdf}
    \includegraphics[width=0.45\textwidth]{figures/Pal13_post_corner.pdf}
    \includegraphics[width=0.4\textwidth]{figures/Pal4_ims_post.pdf}
    \hspace{1cm}
    \includegraphics[width=0.4\textwidth]{figures/Pal13_ims_post.pdf}
    \caption{Caption}
    \script{plot_gc.py}
    \label{fig:Pal4}
\end{figure*}

\subsection{Dwarfs in the Sculptor Group}
\label{sec:scul}
\subsection{Galaxies in HSC}
\label{sec:hsc}
